New theoretical lower bounds of weak Schur numbers using regular Schur numbers

### 2021-06-01 rapport/schur.tex
Correction coquille

The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. They vertically 
extend a sum-free partition by repeating it and they use an other sum-free partition to color the other half according 
to the line number. This way the "blocks" act as safe areas for each other. We give here an example for \(p = 9\), 
\(q = 4\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) (2 S(2) + 1) + S(2)\), both with Abbott and 
Hanson's construction and with a SF-template which is not included in Abbott and Hanson's construction. In both cases, 
the special color is grey.

>>>>

The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. They vertically 
extend a sum-free partition by repeating it and they use an other sum-free partition to color the other half according 
to the line number. This way the "blocks" act as safe areas for each other. We give here an example for \(p = 4\), 
\(q = 9\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) (2 S(2) + 1) + S(2)\), both with Abbott and 
Hanson's construction and with a SF-template which is not included in Abbott and Hanson's construction. In both cases, 
the special color is grey.
